% !TEX root = ..\main.tex

\KeyWords{Delivery, Efficiency, Robots, Drones, Motorcycles, Sustainability.}
\centeredchapterstyle
\begin{abstract}
    \noindent\textbf{}The growing demand for delivery services, especially in densely populated urban areas, has raised significant concerns regarding the efficiency and speed of deliveries. This study proposes solutions to mitigate the challenges associated with this high demand, aiming to reduce waiting times and improve the customer experience. The main objective of this research is to evaluate the effectiveness of different delivery modalities, including the use of robots, drones, and electric motorcycles, in optimizing productivity and reducing operational and environmental costs.  To achieve these objectives, investigations were conducted both individually and in groups, along with multiple meetings to discuss pertinent topics. Qualitative and quantitative data analysis methods were employed to assess the feasibility and effectiveness of different delivery approaches. The results indicate that the implementation of delivery methods using robots, drones, and electric motorcycles is highly feasible. These approaches have demonstrated the ability to increase delivery efficiency, reduce operational costs, and minimize the environmental impact associated with the transportation of goods.  The adoption of innovative technologies, such as robots, drones, and electric motorcycles, can represent an effective solution to the challenges faced in the delivery sector. In addition to increasing customer satisfaction by reducing waiting times, these solutions also offer significant benefits for companies, including cost reduction and increased net returns. However, further studies are necessary to evaluate the practical implementation and market acceptance of these technologies on a large scale.
\end{abstract}
